Variation in distance between consecutive animal locations

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
Adding more text and reference

Random walks used broadly in biology to characterize animal and cell movement. Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions. [@codling2008random]
- IDEA: so maybe use these distributions for the angles. We might see that there is not much difference in angle movement across individuals? They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances. 
- Also might be intriguing to incorporate the time as a set of multiple random walks? or repeats the velocity value for that number of minutes. Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$). Hence, turning events occur as a Poisson process with rate $\lambda$. **This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose. So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data. 
    - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$

@@

"Location accuracy using radio telemetry may be reduced in tropical forests... conservative distance categories of 100-m increments to beteter represent precision. Time categories: 15, 30, 60, 90 minutes. Then calculated probability of movements made within each distance category within each time category, summed accross each time category to give a final probability for each distance category."

>>>>

Random walks used broadly in biology to characterize animal and cell movement. Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions. [@codling2008random]
- IDEA: so maybe use these distributions for the angles. We might see that there is not much difference in angle movement across individuals? They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances. 
- Also might be intriguing to incorporate the time as a set of multiple random walks? or repeats the velocity value for that number of minutes. Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$). Hence, turning events occur as a Poisson process with rate $\lambda$. **This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose. So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data. 
    - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$
  - Pg11. A correlated random walk, CRW, consisting of a series of independet draws from a step length PDF and a turning angle PDF for each step, a first order markov process.
    - using mean square displacement. The effect of step length variability on MSD can be quite significant.
    - MSD being of interest to ecologists due to its relation with the diffusion coefficient D. equations 2.13 and 2.14
** Should write a conclusion about this paper**

# Kareiva Shigesada paper [@kareiva1983analyzing]

We focus here on developing a process to analyze animal movement sequences based on movement lengths, or step lengths, and turning angle probability distributions. Following the methods of Kareiva and Shigesada [-@kareiva1983analyzing], we assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.

@@

"Location accuracy using radio telemetry may be reduced in tropical forests... conservative distance categories of 100-m increments to better represent precision. Time categories: 15, 30, 60, 90 minutes. Then calculated probability of movements made within each distance category within each time category, summed across each time category to give a final probability for each distance category."
